 

### 2021-01-26 vertical-thermal-review.Rmd
knit in new schematic
#27

![**Figure 1. (schematic of a forest summarizing most important gradients--sort of a "graphical abstract".** Current version is just a very rough sketch of how this might look – needs to be filled in with content from the review. We could have a set of arrows for each of the major categories considered here. This would be a key figure, and should be beautifully illustrated—KAT could do a watercolor, or Nidhi could illustrate- and make use of NewPhyt's figure editing service for Tansley reviews). ](schematic/schematic.png)

![rough figure 1., needs some suggestions and info to include.] (https://github.com/EcoClimLab/vertical-thermal-review/blob/master/schematic/vertical%20thermal%20sensitivity%20image.png)

Martijn : in this illustration it would also be nice to show that you can have shade leaves of canopy trees in the understory, and shaded plants of understory species.

>>>>

![**Figure 1. DRAFT schematic of a forest summarizing most important gradients--sort of a "graphical abstract".** . ](schematic/vertical thermal sensitivity image.png)
